Formalization of Abstract Rewriting

### 2025-02-22 Relations/Paper/Definitions.tex

@@

   A relation $R$ has the \emph{weak minimal form property} (WMFP) if every $a \in A$ has the $R$-weak minimal form property.
\end{definition}

>>>>

\begin{definition}\label{d:RP}
    A relation $R$ has the \emph{recurrence property} (RP) if every bounded, increasing sequence 
    has an element $a \in MF$.
\end{definition}

\begin{definition}\label{d:RP-}
    A relation $R$ has the \emph{weak recurrence property} (RP-) if for every increasing 
    sequence with bound $a$, there is an element $i$ of the sequence such that 
    $a \mstep f(i)$.
\end{definition}

@@

   A relation $R$ has the \emph{weak minimal form property} (WMFP) if every $a \in A$ has the $R$-weak minimal form property.
\end{definition}
\begin{definition}
    \label{d:inc}
    A relation $R \sse A \times A$ is called \emph{increasing} if there
    exists a ``size function'' $|-| : A \to \nat$ satisfying, for all $x, y \in A$,
    \[ Rxy \to |x| < |y| \]
\end{definition}
